---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


**NOTE: This is a toy package created for expository purposes, for the second edition of [R Packages](https://r-pkgs.org). It is not meant to actually be useful. If you want a package for factor handling, please see [stringr](https://stringr.tidyverse.org), [stringi](https://stringi.gagolewski.com/),
[rex](https://cran.r-project.org/package=rex), and
[rematch2](https://cran.r-project.org/package=rematch2).**




# Rpkg

<!-- badges: start -->
<!-- badges: end -->

This is a toy R package created for practice in DSCI 310. It provides a simple and safe wrapper around `stringr::str_split()` for splitting a single string into parts.

## Installation

You can install the development version of Rpkg from [GitHub](https://github.com/) with:
      
``` r
# install.packages("devtools")
devtools::install_github("yw-luo/dsci310_a5")
```

## Usage

A fairly common task when dealing with strings is the need to split a single string into many parts.
This is what `base::strsplit()` and `stringr::str_split()` do.

```{r}
library(Rpkg)

# Split a string normally
str_split_one("a,b,c", ",")

# Limit number of splits
str_split_one("a,b,c", ",", n = 2)

# Use fixed pattern for dots
str_split_one("192.168.0.1", stringr::fixed("."))
```

Notice how the return value is a **list** of length one, where the first element holds the character vector of parts.
Often the shape of this output is inconvenient, i.e. we want the un-listed version.

That's exactly what `Rpkg::str_split_one()` does.

```{r}
(x <- "alfa,bravo,charlie,delta")
str_split_one(x, pattern = ",")
```

Use `str_split_one()` when the input is known to be a single string.
For safety, it will error if its input has length greater than one.

`str_split_one()` is built on `stringr::str_split()`, so you can use its `n` argument and stringr's general interface for describing the `pattern` to be matched.

```{r}
str_split_one(x, pattern = ",", n = 2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```